Tropical Andes frugivore trait data Frugivoria

### 2023-07-18 code/L0/L0_TropicalAndes_frugivores_frugivoria_traits.Rmd
inital commit add code from edi repo

```{r}

>>>>

# Retrive Frugivoria data
Using r code provided at https://portal.edirepository.org/nis/codeGeneration?packageId=edi.1220.6&statisticalFileType=r
```{r}
# Package ID: edi.1220.6 Cataloging System:https://pasta.edirepository.org.
# Data set title: Frugivoria: A trait database for birds and mammals exhibiting frugivory across contiguous Neotropical moist forests .
# Data set creator:  Beth Gerstner - Michigan State University 
# Data set creator:  Phoebe Zarnetske - Michigan State University 
# Data set creator:  Patrick Bills - Michigan State University 
# Contact:  Beth Gerstner -  Michigan State University  - gerstn11@msu.edu
# Stylesheet v2.11 for metadata conversion into program: John H. Porter, Univ. Virginia, jporter@virginia.edu

inUrl1  <- "https://pasta.lternet.edu/package/data/eml/edi/1220/6/f2503359fb87b67d22e4a9a33f014107" 
infile1 <- tempfile()
try(download.file(inUrl1,infile1,method="curl"))
if (is.na(file.size(infile1))) download.file(inUrl1,infile1,method="auto")

 dt1 <-read.csv(infile1,header=F 
          ,skip=1
            ,sep=","  
                ,quot='"' 
        , col.names=c(
                    "IUCN_species_name",     
                    "taxonid",     
                    "common_name",     
                    "family",     
                    "genus",     
                    "species",     
                    "subspecies",     
                    "rank",     
                    "elton_species_name",     
                    "taxonomic_disparity",     
                    "species_notes",     
                    "diet_inv_e",     
                    "diet_vend_e",     
                    "diet_vect_e",     
                    "diet_vfish_e",     
                    "diet_vunk_e",     
                    "diet_scav_e",     
                    "diet_fruit_e",     
                    "diet_nect_e",     
                    "diet_seed_e",     
                    "diet_plant_e",     
                    "diet_cat",     
                    "diet_source_e",     
                    "diet_certainty_e",     
                    "diet_breadth",     
                    "diet_level",     
                    "for_strat_value_e",     
                    "for_strat_certainty_e",     
                    "activity_nocturnal_e",     
                    "activity_crepuscular_e",     
                    "activity_diurnal_e",     
                    "activity_source_e",     
                    "activity_certainty_e",     
                    "activity_level",     
                    "body_mass_e",     
                    "body_mass_notes",     
                    "body_mass_level_e",     
                    "body_mass_source_e",     
                    "min_body_size_mm",     
                    "max_body_size_mm",     
                    "body_size_mm",     
                    "body_size_notes",     
                    "body_size_level",     
                    "body_size_source",     
                    "sexual_dimorphism",     
                    "sexual_dimorphism_notes",     
                    "sexual_dimorphism_level",     
                    "sexual_dimorphism_source",     
                    "min_longevity",     
                    "max_longevity",     
                    "longevity",     
                    "longevity_notes",     
                    "longevity_level",     
                    "longevity_source",     
                    "min_home_range",     
                    "max_home_range",     
                    "home_range_size",     
                    "home_range_notes",     
                    "home_range_level",     
                    "home_range_source",     
                    "habitat_specialization",     
                    "habitat_specialization_notes",     
                    "habitat_specialization_source",     
                    "min_generation_time",     
                    "max_generation_time",     
                    "generation_time",     
                    "generation_time_notes",     
                    "generation_time_level",     
                    "generation_time_source",     
                    "IUCN_category",     
                    "habitat",     
                    "habitat_suitability_montane",     
                    "habitat_suitability_lowland",     
                    "habitat_season_montane",     
                    "habitat_season_lowland",     
                    "habitat_major_importance_montane",     
                    "habitat_major_importance_lowland",     
                    "habitat_breadth",     
                    "habitat_breadth_source",     
                    "habitat_level",     
                    "mean_CHELSA_bio1_1981.2010_V.2.1",     
                    "mean_CHELSA_bio12_1981.2010_V.2.1",     
                    "mean_human_fp_range_2010",     
                    "mean_human_fp_range_2020",     
                    "percent_change_hf_2010_2020",     
                    "observed_range_sqkm",     
                    "inferred_range_sqkm",     
                    "date_data_obtained",     
                    "filled_by",     
                    "MSW05_order_p",     
                    "MSW05_family_p",     
                    "MSW05_genus_p",     
                    "MSW05_species_p",     
                    "PanTHERIA_level",     
                    "activity_cycle_p",     
                    "adult_body_mass_g_p",     
                    "adult_forearm_len_mm_p",     
                    "adult_head_body_len_mm_p",     
                    "age_at_eye_opening_d_p",     
                    "age_at_first_birth_d_p",     
                    "basal_met_rate_mLO2hr_p",     
                    "basal_met_rate_mass_g_p",     
                    "diet_breadth_p",     
                    "dispersal_age_d_p",     
                    "gestation_len_d_p",     
                    "habitat_breadth_p",     
                    "home_range_km2_p",     
                    "home_range_indiv_km2_p",     
                    "Inter_birth_interval_d_p",     
                    "litter_size_p",     
                    "litters_per_year_p",     
                    "max_longevity_m_p",     
                    "neonate_body_mass_g_p",     
                    "neonate_head_body_len_mm_p",     
                    "population_density_n.km2_p",     
                    "population_grp_size_p",     
                    "sexual_maturity_age_d_p",     
                    "social_grp_size_p",     
                    "teat_number_p",     
                    "terrestriality_p",     
                    "trophic_level_p",     
                    "weaning_age_d_p",     
                    "weaning_body_mass_g_p",     
                    "weaning_head_body_len_mm_p",     
                    "references_p",     
                    "adult_body_mass_g_EXT_p",     
                    "litters_per_year_EXT_p",     
                    "neonate_body_mass_g_EXT_p",     
                    "weaning_body_mass_g_EXT_p",     
                    "GR_area_km2_p",     
                    "GR_max_lat_dd_p",     
                    "GR_min_lat_dd_p",     
                    "GR_mid_range_lat_dd_p",     
                    "GR_max_long_dd_p",     
                    "GR_min_long_dd_p",     
                    "GR_mid_range_long_dd_p",     
                    "hu_pop_den_min_n.km2_p_OD",     
                    "hu_pop_den_mean_n.km2_p_OD",     
                    "hu_pop_den_5p_n.km2_p_OD",     
                    "hu_pop_den_change_p_OD",     
                    "precip_mean_mm_p_OD",     
                    "temp_mean_01degC_p_OD",     
                    "AET_mean_mm_p_OD",     
                    "PET_mean_mm_p_OD"    ), check.names=TRUE)

unlink(infile1)

# Fix any interval or ratio columns mistakenly read in as nominal and nominal columns read as numeric or dates read as strings

if (class(dt1$IUCN_species_name)!="factor") dt1$IUCN_species_name<- as.factor(dt1$IUCN_species_name)
if (class(dt1$taxonid)=="factor") dt1$taxonid <-as.numeric(levels(dt1$taxonid))[as.integer(dt1$taxonid) ]               
if (class(dt1$taxonid)=="character") dt1$taxonid <-as.numeric(dt1$taxonid)
if (class(dt1$common_name)!="factor") dt1$common_name<- as.factor(dt1$common_name)
if (class(dt1$family)!="factor") dt1$family<- as.factor(dt1$family)
if (class(dt1$genus)!="factor") dt1$genus<- as.factor(dt1$genus)
if (class(dt1$species)!="factor") dt1$species<- as.factor(dt1$species)
if (class(dt1$subspecies)!="factor") dt1$subspecies<- as.factor(dt1$subspecies)
if (class(dt1$rank)!="factor") dt1$rank<- as.factor(dt1$rank)
if (class(dt1$elton_species_name)!="factor") dt1$elton_species_name<- as.factor(dt1$elton_species_name)
if (class(dt1$taxonomic_disparity)!="factor") dt1$taxonomic_disparity<- as.factor(dt1$taxonomic_disparity)
if (class(dt1$species_notes)!="factor") dt1$species_notes<- as.factor(dt1$species_notes)
if (class(dt1$diet_inv_e)=="factor") dt1$diet_inv_e <-as.numeric(levels(dt1$diet_inv_e))[as.integer(dt1$diet_inv_e) ]               
if (class(dt1$diet_inv_e)=="character") dt1$diet_inv_e <-as.numeric(dt1$diet_inv_e)
if (class(dt1$diet_vend_e)=="factor") dt1$diet_vend_e <-as.numeric(levels(dt1$diet_vend_e))[as.integer(dt1$diet_vend_e) ]               
if (class(dt1$diet_vend_e)=="character") dt1$diet_vend_e <-as.numeric(dt1$diet_vend_e)
if (class(dt1$diet_vect_e)=="factor") dt1$diet_vect_e <-as.numeric(levels(dt1$diet_vect_e))[as.integer(dt1$diet_vect_e) ]               
if (class(dt1$diet_vect_e)=="character") dt1$diet_vect_e <-as.numeric(dt1$diet_vect_e)
if (class(dt1$diet_vfish_e)=="factor") dt1$diet_vfish_e <-as.numeric(levels(dt1$diet_vfish_e))[as.integer(dt1$diet_vfish_e) ]               
if (class(dt1$diet_vfish_e)=="character") dt1$diet_vfish_e <-as.numeric(dt1$diet_vfish_e)
if (class(dt1$diet_vunk_e)=="factor") dt1$diet_vunk_e <-as.numeric(levels(dt1$diet_vunk_e))[as.integer(dt1$diet_vunk_e) ]               
if (class(dt1$diet_vunk_e)=="character") dt1$diet_vunk_e <-as.numeric(dt1$diet_vunk_e)
if (class(dt1$diet_scav_e)=="factor") dt1$diet_scav_e <-as.numeric(levels(dt1$diet_scav_e))[as.integer(dt1$diet_scav_e) ]               
if (class(dt1$diet_scav_e)=="character") dt1$diet_scav_e <-as.numeric(dt1$diet_scav_e)
if (class(dt1$diet_fruit_e)=="factor") dt1$diet_fruit_e <-as.numeric(levels(dt1$diet_fruit_e))[as.integer(dt1$diet_fruit_e) ]               
if (class(dt1$diet_fruit_e)=="character") dt1$diet_fruit_e <-as.numeric(dt1$diet_fruit_e)
if (class(dt1$diet_nect_e)=="factor") dt1$diet_nect_e <-as.numeric(levels(dt1$diet_nect_e))[as.integer(dt1$diet_nect_e) ]               
if (class(dt1$diet_nect_e)=="character") dt1$diet_nect_e <-as.numeric(dt1$diet_nect_e)
if (class(dt1$diet_seed_e)=="factor") dt1$diet_seed_e <-as.numeric(levels(dt1$diet_seed_e))[as.integer(dt1$diet_seed_e) ]               
if (class(dt1$diet_seed_e)=="character") dt1$diet_seed_e <-as.numeric(dt1$diet_seed_e)
if (class(dt1$diet_plant_e)=="factor") dt1$diet_plant_e <-as.numeric(levels(dt1$diet_plant_e))[as.integer(dt1$diet_plant_e) ]               
if (class(dt1$diet_plant_e)=="character") dt1$diet_plant_e <-as.numeric(dt1$diet_plant_e)
if (class(dt1$diet_cat)!="factor") dt1$diet_cat<- as.factor(dt1$diet_cat)
if (class(dt1$diet_source_e)!="factor") dt1$diet_source_e<- as.factor(dt1$diet_source_e)
if (class(dt1$diet_certainty_e)!="factor") dt1$diet_certainty_e<- as.factor(dt1$diet_certainty_e)
if (class(dt1$diet_breadth)=="factor") dt1$diet_breadth <-as.numeric(levels(dt1$diet_breadth))[as.integer(dt1$diet_breadth) ]               
if (class(dt1$diet_breadth)=="character") dt1$diet_breadth <-as.numeric(dt1$diet_breadth)
if (class(dt1$diet_level)!="factor") dt1$diet_level<- as.factor(dt1$diet_level)
if (class(dt1$for_strat_value_e)!="factor") dt1$for_strat_value_e<- as.factor(dt1$for_strat_value_e)
if (class(dt1$for_strat_certainty_e)!="factor") dt1$for_strat_certainty_e<- as.factor(dt1$for_strat_certainty_e)
if (class(dt1$activity_nocturnal_e)!="factor") dt1$activity_nocturnal_e<- as.factor(dt1$activity_nocturnal_e)
if (class(dt1$activity_crepuscular_e)!="factor") dt1$activity_crepuscular_e<- as.factor(dt1$activity_crepuscular_e)
if (class(dt1$activity_diurnal_e)!="factor") dt1$activity_diurnal_e<- as.factor(dt1$activity_diurnal_e)
if (class(dt1$activity_source_e)!="factor") dt1$activity_source_e<- as.factor(dt1$activity_source_e)
if (class(dt1$activity_certainty_e)!="factor") dt1$activity_certainty_e<- as.factor(dt1$activity_certainty_e)
if (class(dt1$activity_level)!="factor") dt1$activity_level<- as.factor(dt1$activity_level)
if (class(dt1$body_mass_e)=="factor") dt1$body_mass_e <-as.numeric(levels(dt1$body_mass_e))[as.integer(dt1$body_mass_e) ]               
if (class(dt1$body_mass_e)=="character") dt1$body_mass_e <-as.numeric(dt1$body_mass_e)
if (class(dt1$body_mass_notes)!="factor") dt1$body_mass_notes<- as.factor(dt1$body_mass_notes)
if (class(dt1$body_mass_level_e)!="factor") dt1$body_mass_level_e<- as.factor(dt1$body_mass_level_e)
if (class(dt1$body_mass_source_e)!="factor") dt1$body_mass_source_e<- as.factor(dt1$body_mass_source_e)
if (class(dt1$min_body_size_mm)=="factor") dt1$min_body_size_mm <-as.numeric(levels(dt1$min_body_size_mm))[as.integer(dt1$min_body_size_mm) ]               
if (class(dt1$min_body_size_mm)=="character") dt1$min_body_size_mm <-as.numeric(dt1$min_body_size_mm)
if (class(dt1$max_body_size_mm)=="factor") dt1$max_body_size_mm <-as.numeric(levels(dt1$max_body_size_mm))[as.integer(dt1$max_body_size_mm) ]               
if (class(dt1$max_body_size_mm)=="character") dt1$max_body_size_mm <-as.numeric(dt1$max_body_size_mm)
if (class(dt1$body_size_mm)=="factor") dt1$body_size_mm <-as.numeric(levels(dt1$body_size_mm))[as.integer(dt1$body_size_mm) ]               
if (class(dt1$body_size_mm)=="character") dt1$body_size_mm <-as.numeric(dt1$body_size_mm)
if (class(dt1$body_size_notes)!="factor") dt1$body_size_notes<- as.factor(dt1$body_size_notes)
if (class(dt1$body_size_level)!="factor") dt1$body_size_level<- as.factor(dt1$body_size_level)
if (class(dt1$body_size_source)!="factor") dt1$body_size_source<- as.factor(dt1$body_size_source)
if (class(dt1$sexual_dimorphism)!="factor") dt1$sexual_dimorphism<- as.factor(dt1$sexual_dimorphism)
if (class(dt1$sexual_dimorphism_notes)!="factor") dt1$sexual_dimorphism_notes<- as.factor(dt1$sexual_dimorphism_notes)
if (class(dt1$sexual_dimorphism_level)!="factor") dt1$sexual_dimorphism_level<- as.factor(dt1$sexual_dimorphism_level)
if (class(dt1$sexual_dimorphism_source)!="factor") dt1$sexual_dimorphism_source<- as.factor(dt1$sexual_dimorphism_source)
if (class(dt1$min_longevity)=="factor") dt1$min_longevity <-as.numeric(levels(dt1$min_longevity))[as.integer(dt1$min_longevity) ]               
if (class(dt1$min_longevity)=="character") dt1$min_longevity <-as.numeric(dt1$min_longevity)
if (class(dt1$max_longevity)=="factor") dt1$max_longevity <-as.numeric(levels(dt1$max_longevity))[as.integer(dt1$max_longevity) ]               
if (class(dt1$max_longevity)=="character") dt1$max_longevity <-as.numeric(dt1$max_longevity)
if (class(dt1$longevity)=="factor") dt1$longevity <-as.numeric(levels(dt1$longevity))[as.integer(dt1$longevity) ]               
if (class(dt1$longevity)=="character") dt1$longevity <-as.numeric(dt1$longevity)
if (class(dt1$longevity_notes)!="factor") dt1$longevity_notes<- as.factor(dt1$longevity_notes)
if (class(dt1$longevity_level)!="factor") dt1$longevity_level<- as.factor(dt1$longevity_level)
if (class(dt1$longevity_source)!="factor") dt1$longevity_source<- as.factor(dt1$longevity_source)
if (class(dt1$min_home_range)=="factor") dt1$min_home_range <-as.numeric(levels(dt1$min_home_range))[as.integer(dt1$min_home_range) ]               
if (class(dt1$min_home_range)=="character") dt1$min_home_range <-as.numeric(dt1$min_home_range)
if (class(dt1$max_home_range)=="factor") dt1$max_home_range <-as.numeric(levels(dt1$max_home_range))[as.integer(dt1$max_home_range) ]               
if (class(dt1$max_home_range)=="character") dt1$max_home_range <-as.numeric(dt1$max_home_range)
if (class(dt1$home_range_size)=="factor") dt1$home_range_size <-as.numeric(levels(dt1$home_range_size))[as.integer(dt1$home_range_size) ]               
if (class(dt1$home_range_size)=="character") dt1$home_range_size <-as.numeric(dt1$home_range_size)
if (class(dt1$home_range_notes)!="factor") dt1$home_range_notes<- as.factor(dt1$home_range_notes)
if (class(dt1$home_range_level)!="factor") dt1$home_range_level<- as.factor(dt1$home_range_level)
if (class(dt1$home_range_source)!="factor") dt1$home_range_source<- as.factor(dt1$home_range_source)
if (class(dt1$habitat_specialization)!="factor") dt1$habitat_specialization<- as.factor(dt1$habitat_specialization)
if (class(dt1$habitat_specialization_notes)!="factor") dt1$habitat_specialization_notes<- as.factor(dt1$habitat_specialization_notes)
if (class(dt1$habitat_specialization_source)!="factor") dt1$habitat_specialization_source<- as.factor(dt1$habitat_specialization_source)
if (class(dt1$min_generation_time)=="factor") dt1$min_generation_time <-as.numeric(levels(dt1$min_generation_time))[as.integer(dt1$min_generation_time) ]               
if (class(dt1$min_generation_time)=="character") dt1$min_generation_time <-as.numeric(dt1$min_generation_time)
if (class(dt1$max_generation_time)=="factor") dt1$max_generation_time <-as.numeric(levels(dt1$max_generation_time))[as.integer(dt1$max_generation_time) ]               
if (class(dt1$max_generation_time)=="character") dt1$max_generation_time <-as.numeric(dt1$max_generation_time)
if (class(dt1$generation_time)=="factor") dt1$generation_time <-as.numeric(levels(dt1$generation_time))[as.integer(dt1$generation_time) ]               
if (class(dt1$generation_time)=="character") dt1$generation_time <-as.numeric(dt1$generation_time)
if (class(dt1$generation_time_notes)!="factor") dt1$generation_time_notes<- as.factor(dt1$generation_time_notes)
if (class(dt1$generation_time_level)!="factor") dt1$generation_time_level<- as.factor(dt1$generation_time_level)
if (class(dt1$generation_time_source)!="factor") dt1$generation_time_source<- as.factor(dt1$generation_time_source)
if (class(dt1$IUCN_category)!="factor") dt1$IUCN_category<- as.factor(dt1$IUCN_category)
if (class(dt1$habitat)!="factor") dt1$habitat<- as.factor(dt1$habitat)
if (class(dt1$habitat_suitability_montane)!="factor") dt1$habitat_suitability_montane<- as.factor(dt1$habitat_suitability_montane)
if (class(dt1$habitat_suitability_lowland)!="factor") dt1$habitat_suitability_lowland<- as.factor(dt1$habitat_suitability_lowland)
if (class(dt1$habitat_season_montane)!="factor") dt1$habitat_season_montane<- as.factor(dt1$habitat_season_montane)
if (class(dt1$habitat_season_lowland)!="factor") dt1$habitat_season_lowland<- as.factor(dt1$habitat_season_lowland)
if (class(dt1$habitat_major_importance_montane)!="factor") dt1$habitat_major_importance_montane<- as.factor(dt1$habitat_major_importance_montane)
if (class(dt1$habitat_major_importance_lowland)!="factor") dt1$habitat_major_importance_lowland<- as.factor(dt1$habitat_major_importance_lowland)
if (class(dt1$habitat_breadth)=="factor") dt1$habitat_breadth <-as.numeric(levels(dt1$habitat_breadth))[as.integer(dt1$habitat_breadth) ]               
if (class(dt1$habitat_breadth)=="character") dt1$habitat_breadth <-as.numeric(dt1$habitat_breadth)
if (class(dt1$habitat_breadth_source)!="factor") dt1$habitat_breadth_source<- as.factor(dt1$habitat_breadth_source)
if (class(dt1$habitat_level)!="factor") dt1$habitat_level<- as.factor(dt1$habitat_level)
if (class(dt1$mean_CHELSA_bio1_1981.2010_V.2.1)=="factor") dt1$mean_CHELSA_bio1_1981.2010_V.2.1 <-as.numeric(levels(dt1$mean_CHELSA_bio1_1981.2010_V.2.1))[as.integer(dt1$mean_CHELSA_bio1_1981.2010_V.2.1) ]               
if (class(dt1$mean_CHELSA_bio1_1981.2010_V.2.1)=="character") dt1$mean_CHELSA_bio1_1981.2010_V.2.1 <-as.numeric(dt1$mean_CHELSA_bio1_1981.2010_V.2.1)
if (class(dt1$mean_CHELSA_bio12_1981.2010_V.2.1)=="factor") dt1$mean_CHELSA_bio12_1981.2010_V.2.1 <-as.numeric(levels(dt1$mean_CHELSA_bio12_1981.2010_V.2.1))[as.integer(dt1$mean_CHELSA_bio12_1981.2010_V.2.1) ]               
if (class(dt1$mean_CHELSA_bio12_1981.2010_V.2.1)=="character") dt1$mean_CHELSA_bio12_1981.2010_V.2.1 <-as.numeric(dt1$mean_CHELSA_bio12_1981.2010_V.2.1)
if (class(dt1$mean_human_fp_range_2010)=="factor") dt1$mean_human_fp_range_2010 <-as.numeric(levels(dt1$mean_human_fp_range_2010))[as.integer(dt1$mean_human_fp_range_2010) ]               
if (class(dt1$mean_human_fp_range_2010)=="character") dt1$mean_human_fp_range_2010 <-as.numeric(dt1$mean_human_fp_range_2010)
if (class(dt1$mean_human_fp_range_2020)=="factor") dt1$mean_human_fp_range_2020 <-as.numeric(levels(dt1$mean_human_fp_range_2020))[as.integer(dt1$mean_human_fp_range_2020) ]               
if (class(dt1$mean_human_fp_range_2020)=="character") dt1$mean_human_fp_range_2020 <-as.numeric(dt1$mean_human_fp_range_2020)
if (class(dt1$percent_change_hf_2010_2020)=="factor") dt1$percent_change_hf_2010_2020 <-as.numeric(levels(dt1$percent_change_hf_2010_2020))[as.integer(dt1$percent_change_hf_2010_2020) ]               
if (class(dt1$percent_change_hf_2010_2020)=="character") dt1$percent_change_hf_2010_2020 <-as.numeric(dt1$percent_change_hf_2010_2020)
if (class(dt1$observed_range_sqkm)=="factor") dt1$observed_range_sqkm <-as.numeric(levels(dt1$observed_range_sqkm))[as.integer(dt1$observed_range_sqkm) ]               
if (class(dt1$observed_range_sqkm)=="character") dt1$observed_range_sqkm <-as.numeric(dt1$observed_range_sqkm)
if (class(dt1$inferred_range_sqkm)=="factor") dt1$inferred_range_sqkm <-as.numeric(levels(dt1$inferred_range_sqkm))[as.integer(dt1$inferred_range_sqkm) ]               
if (class(dt1$inferred_range_sqkm)=="character") dt1$inferred_range_sqkm <-as.numeric(dt1$inferred_range_sqkm)
if (class(dt1$date_data_obtained)!="factor") dt1$date_data_obtained<- as.factor(dt1$date_data_obtained)
if (class(dt1$filled_by)!="factor") dt1$filled_by<- as.factor(dt1$filled_by)
if (class(dt1$MSW05_order_p)!="factor") dt1$MSW05_order_p<- as.factor(dt1$MSW05_order_p)
if (class(dt1$MSW05_family_p)!="factor") dt1$MSW05_family_p<- as.factor(dt1$MSW05_family_p)
if (class(dt1$MSW05_genus_p)!="factor") dt1$MSW05_genus_p<- as.factor(dt1$MSW05_genus_p)
if (class(dt1$MSW05_species_p)!="factor") dt1$MSW05_species_p<- as.factor(dt1$MSW05_species_p)
if (class(dt1$PanTHERIA_level)!="factor") dt1$PanTHERIA_level<- as.factor(dt1$PanTHERIA_level)
if (class(dt1$activity_cycle_p)!="factor") dt1$activity_cycle_p<- as.factor(dt1$activity_cycle_p)
if (class(dt1$adult_body_mass_g_p)=="factor") dt1$adult_body_mass_g_p <-as.numeric(levels(dt1$adult_body_mass_g_p))[as.integer(dt1$adult_body_mass_g_p) ]               
if (class(dt1$adult_body_mass_g_p)=="character") dt1$adult_body_mass_g_p <-as.numeric(dt1$adult_body_mass_g_p)
if (class(dt1$adult_forearm_len_mm_p)=="factor") dt1$adult_forearm_len_mm_p <-as.numeric(levels(dt1$adult_forearm_len_mm_p))[as.integer(dt1$adult_forearm_len_mm_p) ]               
if (class(dt1$adult_forearm_len_mm_p)=="character") dt1$adult_forearm_len_mm_p <-as.numeric(dt1$adult_forearm_len_mm_p)
if (class(dt1$adult_head_body_len_mm_p)=="factor") dt1$adult_head_body_len_mm_p <-as.numeric(levels(dt1$adult_head_body_len_mm_p))[as.integer(dt1$adult_head_body_len_mm_p) ]               
if (class(dt1$adult_head_body_len_mm_p)=="character") dt1$adult_head_body_len_mm_p <-as.numeric(dt1$adult_head_body_len_mm_p)
if (class(dt1$age_at_eye_opening_d_p)=="factor") dt1$age_at_eye_opening_d_p <-as.numeric(levels(dt1$age_at_eye_opening_d_p))[as.integer(dt1$age_at_eye_opening_d_p) ]               
if (class(dt1$age_at_eye_opening_d_p)=="character") dt1$age_at_eye_opening_d_p <-as.numeric(dt1$age_at_eye_opening_d_p)
if (class(dt1$age_at_first_birth_d_p)=="factor") dt1$age_at_first_birth_d_p <-as.numeric(levels(dt1$age_at_first_birth_d_p))[as.integer(dt1$age_at_first_birth_d_p) ]               
if (class(dt1$age_at_first_birth_d_p)=="character") dt1$age_at_first_birth_d_p <-as.numeric(dt1$age_at_first_birth_d_p)
if (class(dt1$basal_met_rate_mLO2hr_p)=="factor") dt1$basal_met_rate_mLO2hr_p <-as.numeric(levels(dt1$basal_met_rate_mLO2hr_p))[as.integer(dt1$basal_met_rate_mLO2hr_p) ]               
if (class(dt1$basal_met_rate_mLO2hr_p)=="character") dt1$basal_met_rate_mLO2hr_p <-as.numeric(dt1$basal_met_rate_mLO2hr_p)
if (class(dt1$basal_met_rate_mass_g_p)=="factor") dt1$basal_met_rate_mass_g_p <-as.numeric(levels(dt1$basal_met_rate_mass_g_p))[as.integer(dt1$basal_met_rate_mass_g_p) ]               
if (class(dt1$basal_met_rate_mass_g_p)=="character") dt1$basal_met_rate_mass_g_p <-as.numeric(dt1$basal_met_rate_mass_g_p)
if (class(dt1$diet_breadth_p)=="factor") dt1$diet_breadth_p <-as.numeric(levels(dt1$diet_breadth_p))[as.integer(dt1$diet_breadth_p) ]               
if (class(dt1$diet_breadth_p)=="character") dt1$diet_breadth_p <-as.numeric(dt1$diet_breadth_p)
if (class(dt1$dispersal_age_d_p)=="factor") dt1$dispersal_age_d_p <-as.numeric(levels(dt1$dispersal_age_d_p))[as.integer(dt1$dispersal_age_d_p) ]               
if (class(dt1$dispersal_age_d_p)=="character") dt1$dispersal_age_d_p <-as.numeric(dt1$dispersal_age_d_p)
if (class(dt1$gestation_len_d_p)=="factor") dt1$gestation_len_d_p <-as.numeric(levels(dt1$gestation_len_d_p))[as.integer(dt1$gestation_len_d_p) ]               
if (class(dt1$gestation_len_d_p)=="character") dt1$gestation_len_d_p <-as.numeric(dt1$gestation_len_d_p)
if (class(dt1$habitat_breadth_p)=="factor") dt1$habitat_breadth_p <-as.numeric(levels(dt1$habitat_breadth_p))[as.integer(dt1$habitat_breadth_p) ]               
if (class(dt1$habitat_breadth_p)=="character") dt1$habitat_breadth_p <-as.numeric(dt1$habitat_breadth_p)
if (class(dt1$home_range_km2_p)=="factor") dt1$home_range_km2_p <-as.numeric(levels(dt1$home_range_km2_p))[as.integer(dt1$home_range_km2_p) ]               
if (class(dt1$home_range_km2_p)=="character") dt1$home_range_km2_p <-as.numeric(dt1$home_range_km2_p)
if (class(dt1$home_range_indiv_km2_p)=="factor") dt1$home_range_indiv_km2_p <-as.numeric(levels(dt1$home_range_indiv_km2_p))[as.integer(dt1$home_range_indiv_km2_p) ]               
if (class(dt1$home_range_indiv_km2_p)=="character") dt1$home_range_indiv_km2_p <-as.numeric(dt1$home_range_indiv_km2_p)
if (class(dt1$Inter_birth_interval_d_p)=="factor") dt1$Inter_birth_interval_d_p <-as.numeric(levels(dt1$Inter_birth_interval_d_p))[as.integer(dt1$Inter_birth_interval_d_p) ]               
if (class(dt1$Inter_birth_interval_d_p)=="character") dt1$Inter_birth_interval_d_p <-as.numeric(dt1$Inter_birth_interval_d_p)
if (class(dt1$litter_size_p)=="factor") dt1$litter_size_p <-as.numeric(levels(dt1$litter_size_p))[as.integer(dt1$litter_size_p) ]               
if (class(dt1$litter_size_p)=="character") dt1$litter_size_p <-as.numeric(dt1$litter_size_p)
if (class(dt1$litters_per_year_p)=="factor") dt1$litters_per_year_p <-as.numeric(levels(dt1$litters_per_year_p))[as.integer(dt1$litters_per_year_p) ]               
if (class(dt1$litters_per_year_p)=="character") dt1$litters_per_year_p <-as.numeric(dt1$litters_per_year_p)
if (class(dt1$max_longevity_m_p)=="factor") dt1$max_longevity_m_p <-as.numeric(levels(dt1$max_longevity_m_p))[as.integer(dt1$max_longevity_m_p) ]               
if (class(dt1$max_longevity_m_p)=="character") dt1$max_longevity_m_p <-as.numeric(dt1$max_longevity_m_p)
if (class(dt1$neonate_body_mass_g_p)=="factor") dt1$neonate_body_mass_g_p <-as.numeric(levels(dt1$neonate_body_mass_g_p))[as.integer(dt1$neonate_body_mass_g_p) ]               
if (class(dt1$neonate_body_mass_g_p)=="character") dt1$neonate_body_mass_g_p <-as.numeric(dt1$neonate_body_mass_g_p)
if (class(dt1$neonate_head_body_len_mm_p)=="factor") dt1$neonate_head_body_len_mm_p <-as.numeric(levels(dt1$neonate_head_body_len_mm_p))[as.integer(dt1$neonate_head_body_len_mm_p) ]               
if (class(dt1$neonate_head_body_len_mm_p)=="character") dt1$neonate_head_body_len_mm_p <-as.numeric(dt1$neonate_head_body_len_mm_p)
if (class(dt1$population_density_n.km2_p)=="factor") dt1$population_density_n.km2_p <-as.numeric(levels(dt1$population_density_n.km2_p))[as.integer(dt1$population_density_n.km2_p) ]               
if (class(dt1$population_density_n.km2_p)=="character") dt1$population_density_n.km2_p <-as.numeric(dt1$population_density_n.km2_p)
if (class(dt1$population_grp_size_p)=="factor") dt1$population_grp_size_p <-as.numeric(levels(dt1$population_grp_size_p))[as.integer(dt1$population_grp_size_p) ]               
if (class(dt1$population_grp_size_p)=="character") dt1$population_grp_size_p <-as.numeric(dt1$population_grp_size_p)
if (class(dt1$sexual_maturity_age_d_p)=="factor") dt1$sexual_maturity_age_d_p <-as.numeric(levels(dt1$sexual_maturity_age_d_p))[as.integer(dt1$sexual_maturity_age_d_p) ]               
if (class(dt1$sexual_maturity_age_d_p)=="character") dt1$sexual_maturity_age_d_p <-as.numeric(dt1$sexual_maturity_age_d_p)
if (class(dt1$social_grp_size_p)=="factor") dt1$social_grp_size_p <-as.numeric(levels(dt1$social_grp_size_p))[as.integer(dt1$social_grp_size_p) ]               
if (class(dt1$social_grp_size_p)=="character") dt1$social_grp_size_p <-as.numeric(dt1$social_grp_size_p)
if (class(dt1$teat_number_p)=="factor") dt1$teat_number_p <-as.numeric(levels(dt1$teat_number_p))[as.integer(dt1$teat_number_p) ]               
if (class(dt1$teat_number_p)=="character") dt1$teat_number_p <-as.numeric(dt1$teat_number_p)
if (class(dt1$terrestriality_p)!="factor") dt1$terrestriality_p<- as.factor(dt1$terrestriality_p)
if (class(dt1$trophic_level_p)!="factor") dt1$trophic_level_p<- as.factor(dt1$trophic_level_p)
if (class(dt1$weaning_age_d_p)=="factor") dt1$weaning_age_d_p <-as.numeric(levels(dt1$weaning_age_d_p))[as.integer(dt1$weaning_age_d_p) ]               
if (class(dt1$weaning_age_d_p)=="character") dt1$weaning_age_d_p <-as.numeric(dt1$weaning_age_d_p)
if (class(dt1$weaning_body_mass_g_p)=="factor") dt1$weaning_body_mass_g_p <-as.numeric(levels(dt1$weaning_body_mass_g_p))[as.integer(dt1$weaning_body_mass_g_p) ]               
if (class(dt1$weaning_body_mass_g_p)=="character") dt1$weaning_body_mass_g_p <-as.numeric(dt1$weaning_body_mass_g_p)
if (class(dt1$weaning_head_body_len_mm_p)=="factor") dt1$weaning_head_body_len_mm_p <-as.numeric(levels(dt1$weaning_head_body_len_mm_p))[as.integer(dt1$weaning_head_body_len_mm_p) ]               
if (class(dt1$weaning_head_body_len_mm_p)=="character") dt1$weaning_head_body_len_mm_p <-as.numeric(dt1$weaning_head_body_len_mm_p)
if (class(dt1$references_p)!="factor") dt1$references_p<- as.factor(dt1$references_p)
if (class(dt1$adult_body_mass_g_EXT_p)=="factor") dt1$adult_body_mass_g_EXT_p <-as.numeric(levels(dt1$adult_body_mass_g_EXT_p))[as.integer(dt1$adult_body_mass_g_EXT_p) ]               
if (class(dt1$adult_body_mass_g_EXT_p)=="character") dt1$adult_body_mass_g_EXT_p <-as.numeric(dt1$adult_body_mass_g_EXT_p)
